Exploring the Evolution of Energy in Radiohead's Music

### 2024-10-10 paper/paper.qmd
upload files
upload the file

---
title: "Exploring the Evolution of Energy in Radiohead's Music"
subtitle: "Energy Levels Fluctuate Post-2000 with Positive Correlations to Valence and Loudness Across Albums"
author: 
  - Jianing Li
  - Xizi Sun
  - Yawen Tan
  - Shanjie Jiao
  - Xinqi Yue
  - Duanyi Su
thanks: "Code and data are available at: [GitHub repo Link]"
date: today
date-format: long
abstract: "Radiohead's music shows notable variation in energy, valence, and loudness across their discography. This analysis examines the trends in energy levels over time, the distribution of energy across albums, and the relationships between energy, positivity, and loudness. The results indicate that energy levels fluctuate significantly post-2000, with louder and more positive songs tending to have higher energy. Understanding these patterns provides insights into the band's evolving artistic approach and the diversity of their musical output."
format: pdf
number-sections: true
table-of-contents: true
bibliography: references.bib
---

@@

The data and code used in this analysis are publicly available at: [GitHub repo link].

@@

## Data Tools
All data analysis and visualizations were conducted using R [@citeR]. Data was obtained from Spotify using the [@spotifyr] R package. Visualizations were created using the ggplot2 package [@citeGgplot2], with data manipulation carried out via dplyr [@citeDplyr] and tidyr [@citeTidyverse]. PDF file is generated by knitr [@citeKnitr]. Guidance on storytelling with data was drawn from Telling Stories with Data [@tellingstorieswithdata].

>>>>

---
title: "Exploring the Evolution of Energy in Radiohead's Music"
subtitle: "Energy Levels Fluctuate Post-2000 with Positive Correlations to Valence and Loudness Across Albums"
author: 
  - Jianing Li
  - Xizi Sun
  - Yawen Tan
  - Shanjie Jiao
  - Xinqi Yue
  - Duanyi Su
thanks: "Code and data are available at: [https://github.com/YawennnnnnTan/Spotify-Data-Analysis/tree/main]"
date: today
date-format: long
abstract: "Radiohead's music shows notable variation in energy, valence, and loudness across their discography. This analysis examines the trends in energy levels over time, the distribution of energy across albums, and the relationships between energy, positivity, and loudness. The results indicate that energy levels fluctuate significantly around post-2000 and post-2015, with louder and more positive songs tending to have higher energy. Understanding these patterns provides insights into the band's evolving artistic approach and the diversity of their musical output."
format: pdf
number-sections: true
table-of-contents: true
bibliography: references.bib
---

@@

@@

## Data Tools
All data analysis and visualizations were conducted using R [@citeR] and use here [@hereR] package to read data. Data was obtained from Spotify using the [@spotifyr] R package. Visualizations were created using the ggplot2 package [@citeGgplot2], with data manipulation carried out via dplyr [@citeDplyr] and tidyr [@citeTidyverse]. PDF file is generated by knitr [@citeKnitr]. Guidance on storytelling with data was drawn from Telling Stories with Data [@tellingstorieswithdata].
